Low or no cost distributed evolutionary computation

### 2014-08-31 low-or-no-cost-abstract.tex
Some error

\abstract{From the era of big science we are back to the "do it yourself", where you do not have any money to buy clusters or subscribe to grids but still have algorithms that crave many computing nodes and need them to measure scalability. Fortunately, this coincides with the era of big data, cloud computing, and browsers that include JavaScript virtual machines. Those are the reason why this talk will focus on two different aspects of volunteer or freeriding computing: first, the pragmatic: where to find those resources, which ones can be used, what kind of support you have to give them; and then, the theoretical: how evolutionary algorithms can be adapted to a environment in which nodes come and go, have different computing capabilites and operate in complete asynchrony of each other.}

@@

\section{Conclussion}

@@

There are many challenges involved in using these resources: from adapting current algorithms so that they match this environment \cite{agajaj} to check which EA configuration works the best in it, or creating a framework that can use it easily \cite{nodeo2014}. But the main challenge is that asking people to contribute resources implies that you are opening your science to society and you have to give something in return: you have to adopt a set of best practices that have come to be known as Open Science, because ``Give, and it shall be given unto you'', you will get as much back from society as you give to it opening your science and explaining it to the public. This, among other things, means that popularity will become directly performance of the metacomputer you create by attrating more users.

>>>>

\abstract{From the era of big science we are back to the "do it yourself", where you do not have any money to buy clusters or subscribe to grids but still have algorithms that crave many computing nodes and need them to measure scalability. Fortunately, this coincides with the era of big data, cloud computing, and browsers that include JavaScript virtual machines. Those are the reason why this talk will focus on two different aspects of volunteer or freeriding computing: first, the pragmatic: where to find those resources, which ones can be used, what kind of support you have to give them; and then, the theoretical: how evolutionary algorithms can be adapted to a environment in which nodes come and go, have different computing capabilities and operate in complete asynchrony of each other.}

@@

\section{Conclusion}

@@

There are many challenges involved in using these resources: from adapting current algorithms so that they match this environment \cite{agajaj} to check which EA configuration works the best in it, or creating a framework that can use it easily \cite{nodeo2014}. But the main challenge is that asking people to contribute resources implies that you are opening your science to society and you have to give something in return: you have to adopt a set of best practices that have come to be known as Open Science, because ``Give, and it shall be given unto you'', you will get as much back from society as you give to it opening your science and explaining it to the public. This, among other things, means that popularity will become directly performance of the metacomputer you create by attracting more users.
